---
title: "Lab 6"
author: KSRM
output: html_document
---

## Confidence in Submission 

Problem 1: 70 - Worked through Lab 6. I then created the custom function on my own. 


## Results of Randomization 

In the example data, I selected two vectors with varied distributions to test my custom randomization function. The mean difference of the example groups was approximately 7.67. The result of the randomization test indicate that this mean difference is unlikely to occur by chance alone. 

Next, using the intellect ratings for audio and reading groups, the means of these groups were randomized through a monte carlo simulation. The actual mean difference from the data set was approximately 1.98. The results of the randomization test indicate that this mean difference is also unlikely to occur by chance alone. If the observed mean difference had been 0.5, then the data set would have failed the randomization test. 

```{r}
library(dplyr)
library(ggplot2)
the_data <- read.csv("open_data/SchroederEpley2015data.csv", header=TRUE)
colnames(the_data)[1] <- gsub('^...', '',colnames(the_data)[1])

group1 <- c(14,16,12,15,13,14) #example data
group2 <- c(3,3,9,10,4,9)

sample(group2, group2[1:3])
groups <- c(group1, group2)
group_size <- length(group1)
mean_difference <- mean(group1)-mean(group2)
print(mean_difference)

randomization_test <- function (group_1, group_2, n_runs) {
    possible_differences <- c()
    group_size <- length(group_1)
      for (i in 1:n_runs){  
        group_means <- c(group_1,group_2) #combining groups
        group_means <- sample(group_means) #shuffling group means
        randomized_group1 <- mean (group_means[1:group_size])
        randomized_group2 <- mean (group_means[(group_size+1):length(group_means)])

    possible_differences[i] <- randomized_group1-randomized_group2 #saving randomized mean differences
      }
    print(qplot(unlist(possible_differences), xlab= "mean differences", ylab="number of simulations")+
      geom_histogram(color = "orange")+
      geom_vline(xintercept = 0.5, color = "red")+
      theme_classic())
    
    probability <- length(possible_differences[possible_differences>=0.5])/length(possible_differences)
    print(paste("Probability greater than 0.5 =", probability))
}

randomization_test(group1,group2, 1000) #testing custom function

random_group1 <- rnorm(100, 0, 1) #second function test
random_group2 <- rnorm(100, 0, 1)
print(mean(random_group1)-mean(random_group2)) 
randomization_test(random_group1,random_group2, 1000)


audio_rating <- the_data %>%
  filter(CONDITION==1) %>%
  select(Intellect_Rating) 
audio_rating <- as.vector(audio_rating[,"Intellect_Rating"])

reading_rating <- the_data %>%
  filter(CONDITION==0) %>%
  select(Intellect_Rating) 
reading_rating <- as.vector(reading_rating[,"Intellect_Rating"])

randomization_test(audio_rating, reading_rating, 1000)

experimental <- mean(audio_rating)-mean(reading_rating)
print(experimental) #mean difference
```

## For comparison: results of additional randomization based on course lesson

The condition group was randomized, resulting in mean differences between condition group 1 and 2 that did not exceed + or - 2. This randomization test reflects that mean differences close to |+/-2| between condition groups would be unlikely to occur by chance alone. On the other hand, if the experimental mean difference was 0.5 or greater, then there would be a considerable probability of 0.207 that the mean difference was produced by chance alone. 

```{r}
possible_differences <- c()
for (i in 1:1000){
  new_data <- the_data %>%
    mutate(randomizedcondition = sample(CONDITION, 39, replace=TRUE))%>%
    group_by(randomizedcondition)%>%
    summarize(new_mean=mean(Intellect_Rating))
    possible_differences[i] <-new_data[new_data$randomizedcondition==1,]$new_mean-new_data[new_data$randomizedcondition     ==0,]$new_mean
}
qplot(unlist(possible_differences), xlab = "mean differences", ylab = "number of simulations")+
  geom_histogram(color="orange")+
  geom_vline(xintercept=0.5,color="red")+
  theme_classic()
length(possible_differences[possible_differences>=0.5])/length(possible_differences)
```

