---
title: "Lab 11"
author: "KSRM"
date: "12/2/2021"
output: html_document
---

Confidence in Submission:
80 - It was necessary to review permutation versus randomization tests.  

Problem 1 
A. Calculate Pearson's R and associated p-value using cor.test(). 
B. Use a permutation test to create a null-distribution, and report the p-value for getting the observed correlation or larger using your simulated null-distribution.
```{r}
X <- c(1,4,3,2,5,4,3,6,7,8)
Y <- c(1,3,6,7,8,2,8,7,6,9)

results <- cor.test(X, Y)

r1 <- results$estimate # pearson's R
p1 <- results$p.value

null_dist <- replicate(1000, cor(sample(X),sample(Y))) # permute two variables, compute r, replicate

(p2 <- length(null_dist[null_dist >= r1])/1000)

```


Problem 2 
Compute both the smallest and largest possible sum of cross-products using X & Y vectors. 
```{r}
# largest sum of cross-products
sum(sort(X)*sort(Y))

sum(sort(X, decreasing = TRUE)*sort(Y, decreasing = TRUE))

# smallest sum of cross-products
X2 <- sort(X, decreasing = FALSE)
Y2 <- sort(Y, decreasing = TRUE)

sum(X2*Y2)
```

