---
title: "Lab 9"
author: KSRM
output: html_document
---

## Confidence in Submission

80 - To review group by, pivot wider, and creating a matrix from the contingency table. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,          # show both code and output or only output ?
  fig.align = 'center',  # centers graphs on the page,
  out.width = "90%",    # setting width for graphs,
  warning = FALSE,      # include warnings/messages from console ?
  message = FALSE, 
  size = "small"       # setting size of LaTex output
  )

library(readxl)
library(tibble)
```

## Silver et al.'s experiment 1 results (Silver et al., 2020, p. 1424)

## Binomial test

The two-tailed binomial test resulted in a p-value of 0.026, suggesting that the choice of toy followed more than chance. 

## Two chi squared tests. 

Silver et al. found no significant relationships between infants choices and age or gender. The results of the two chi squared tests of independence were as follows:

Nineteen degrees of freedom for the age variable. 
$$ 
\chi^2(19, N = 21) = 18.24
$$
One degree of freedom for the gender variable. 
$$ 
\chi^2(1, N = 21) = 0.696
$$

## Re-analysis of research results. 

I was able to reproduce the results for the binomial test with a p-value of 0.0266, indicating that it is unlikely that infants chose novel cubes due to chance alone. 
```{r}
paper <- read_excel("When not choosing leads to not liking_Data.xlsx")

tibble(paper)
colnames(paper) 

(colnames(paper) <- gsub(" ", "_", colnames(paper)))

#reproduce the binomial test 
library(dplyr)

e1 <- paper %>%
  filter(ExperimentNumber == "1")

number_chose_C <- sum(e1$Infant_Chose_C)

binom.test(x = number_chose_C,
           n = dim(e1)[1],
           p = .5,
           alternative = "two.sided")


# applying pbinom - rstats notes
total_C <- length(e1$Infant_Chose_C)
(binomial_p <- pbinom(q = total_C - number_chose_C,
                      size = total_C, 
                      prob = .5, 
                      lower.tail = TRUE)*2)
  
```


## Reproduce the chi-squared test for categorical variables gender and toy choice

I obtained the same chi-squared value of 0.15273 and p-value of 0.6959, indicating no relationship between gender and toy choice.  
```{r}
library(tidyr)

# frequency crosstab
gender_crosstab <- table(e1$Infant_Chose_C, e1$Gender)

# frequency table using dplyr - rstats notes
gender_choice_table <- e1 %>%
  group_by(Gender, Infant_Chose_C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(Gender),
              values_from = counts)

# running chi squared test
chisq.test(gender_crosstab, correct = FALSE)


chisq.test(gender_choice_table[,2:3], correct = FALSE)
(gender_chi <- chisq.test(gender_choice_table[,2:3]))
uncorrected_gender_chi_sq <- sum((gender_chi$observed-gender_chi$expected)^2/gender_chi$expected)

(gender_chi_sq_unc <- pchisq(uncorrected_gender_chi_sq,df = 1,lower.tail = FALSE))# p-value 
```

## Reproduce the chi-squared test for transformed variable age and toy choice

I obtained the same chi-squared value of 18.244 and p-value of 0.5062, indicating no relationship between age as a factor variable and toy choice. 
```{r}
age_crosstab <- table(e1$AgeMonths, e1$Infant_Chose_C)
(chisq.test(age_crosstab, correct = FALSE))

#rstats solution
age_table <- e1 %>%
  group_by(AgeMonths, Infant_Chose_C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(AgeMonths),
              values_from = counts)
age_table[is.na(age_table)] <- 0
age_table <- as.matrix(age_table[,2:21])
(age_xs <- chisq.test(age_table))
```


