---
title: "Lab 5"
author: KSRM
output: html_document
---

## Confidence in Submission 

Problem 1:5 - 90 I can complete on my own. I am not sure why it is not possible to confirm answers for problem 3 and 4 using sample z-scores and pnorm. 


Problem 1 - Take a million observations from the normal distribution and determine which proportion of numbers are larger than 2.5 

0.6% of numbers from the normal distribution will be greater than 2.5. Under the right tail of the normal density curve, between 0.5% and 2.5% of numbers will fall between 3 sd and 2 sd, respectively. 
```{r}
my_sample <- rnorm(1000000, 0, 1)

sum(my_sample>2.5)/sum(my_sample==my_sample)

#confirm using pnorm
1-pnorm(2.5, 0, 1)
```


Problem 2 - Given a distribution of 10,000 test scores with a mean = 100 and sd = 10, how many scores will fall over +3 standard deviations ?

Approximately one. 
```{r}
test_scores <- rnorm(10, 100, 10)
z_scores <- (test_scores-100)/10
length(z_scores>3)/10 #99% of scores are under 3 sds in a normal distribution

#confirm using pnorm
1-pnorm(3, 100, 10)
```


Problem 3 - A random sample of 25 observations has a mean = 12. The sample is derived from a normal distribution with mean = 10 and sd = 20. What is the probability of receiving a sample from this distribution of mean >=12 ? 

Approximately 30.05% of sample means will be 12 or greater from this distribution. 
```{r}
library(ggplot2)
sampling_distribution <- replicate(10000, mean((rnorm(25, 10, 20))))

ggplot() +
  geom_histogram(aes(sampling_distribution)) +
  geom_vline(xintercept = 12,color="red")

sum(sampling_distribution>=12)/sum(sampling_distribution==sampling_distribution)


(z_score <- (12-10)/(20/sqrt(25)))
1-pnorm(0.5, 10, 20)

sd(rnorm(25, 10, 20))
```


Problem 4 - A random sample of 100 observations has a mean = 12. The sample is derived from a normal distribution with mean = 10 and sd = 20. What is the probability of receiving a sample from this distribution of mean >=12 ? 

Approximately 16.24% of scores will be 12 or greater from this distribution. Less sample means will be greater or equal to 12 than in the prior example, because there is less variation in the greater population or distribution. By taking the mean of 100 numbers instead of 25, the variability of the data set is lessened. 
```{r}
sampling_distribution <- replicate(10000, mean((rnorm(100, 10, 20))))

ggplot() +
  geom_histogram(aes(sampling_distribution)) +
  geom_vline(xintercept = 12,color="red")

sum(sampling_distribution>=12)/sum(sampling_distribution==sampling_distribution)


sd(sampling_distribution)
(z_score <- (12-10)/(20/sqrt(100)))
1-pnorm(1, 10, 20) 

sd(rnorm(100, 10, 20))
```


Problem 5 - A random sample of 25 observations has a sd = 15. The sample is derived from a normal distribution with mean = 10 and sd = 20. What is the probability of receiving a sample sd from this distribution of sd <=15 ? 

The probability of getting a sample sd of <=15 is 0.0431. There is less variability averaged across the sampling distribution of sampled standard deviations.

```{r}
sampling_distribution <- replicate(10000, sd(rnorm(25, 10, 20)))

ggplot() +
  geom_histogram(aes(sampling_distribution)) +
  geom_vline(xintercept = 15,color="red")

sum(sampling_distribution<=15)/sum(sampling_distribution==sampling_distribution)


#comparison of single sample sd and sampling distribution sd
sd(rnorm(25, 10, 20)) 
average_sd <- mean(sampling_distribution) 

```

