---
title: "Lab 10"
author: "KSRM"
date: "11/17/2021"
output: html_document
---

Confidence in Submission

0 - use of rstats solution
Stumped by why it is not possible to take the mean of already detected variables.


Data preparation.
Overview: Experiment 3 data (Rosenbaum et al., 2017) consists of paired samples, n = 50 observations where participants were exposed to congruent and incongruent stimuli under both standing and sitting conditions.  
```{r}
library(tibble)
library(tidyr)
library(dplyr)
library(ggplot2)

stroop_stand <- read.csv("open_data/stroop_stand.csv")

colnames(stroop_stand)[1] <- "congruent_stand"
dim(stroop_stand)

(test_condition <- colnames(stroop_stand))

tibble(stroop_stand)
```


1. Reproduce as much of the analysis as possible using only paired-sample t-tests. Note, the authors reported a 2x2 repeated measures ANOVA, but consider how the same questions could be answered by t-tests (2 points)
```{r}
# r stats solution
# Stand Stroop effect
(stand_stroop <- t.test(stroop_stand$incongruent_stand,
       stroop_stand$congruent_stand,
       paired = TRUE))
# Sit Stroop effect
(sit_stroop <- t.test(stroop_stand$incongruent_sit,
       stroop_stand$congruent_sit,
       paired = TRUE))
```


2.Reproduce a graph of the means, like shown in the paper (2 points)
```{r}
# r stats solution
stroop_df <- stroop_stand %>%
  pivot_longer(cols = 1:4,
               names_to = c("Congruency","Posture"),
               names_sep = "_",
               values_to = "RTs")
# get means
overall_means <- stroop_df %>%
                  group_by(Posture,Congruency) %>%
                  summarise(meanRT = mean(RTs),
                            SEMRT = (sd(RTs)/sqrt(length(RTs))))

# plot
ggplot(overall_means, aes(x=Posture,
                          y=meanRT, 
                          group=Congruency,
                          fill=Congruency))+
  geom_bar(stat="identity",position="dodge")+
  theme_classic(base_size=12)+
  ylab("Mean Reaction Time (ms)")+
  geom_errorbar(aes(ymin=meanRT-SEMRT,
                    ymax=meanRT+SEMRT),
                position=position_dodge(width=0.9),
                width=.2,
                color="black")+
  coord_cartesian(ylim=c(500,1000))
```

3. Present a power-curve analysis for the design. (2 points)
```{r}
# rstats code 

effect_sizes <- seq(0,1.5,.1)
prop_significant <-c()
for(i in 1:length(effect_sizes)){
  sim_ps <- replicate(1000, t.test(replicate(50, rnorm(1, effect_sizes[i], 1)),
                                   mu = 0)$p.value)
  
  prop_significant[i] <- length(sim_ps[sim_ps < .05])/1000
}
plot_df <- data.frame(effect_sizes,
                      prop_significant)
ggplot(plot_df, aes(x=effect_sizes,y=prop_significant))+
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks=seq(0,1.5,.1))+
  scale_y_continuous(breaks=seq(0,1,.1)) +
  ylab("Proportion Significant")
```



