---
title: "Lab 3"
output: html_document
---
```{r}
library(ggplot2)
library(dplyr)
```

Create five samples of 25 observations from a normal distribution with mean 200, and standard deviation 100. Compute the mean of each sample, and plot the means in a graph using ggplot2. (1 point)

```{r}
observations<-rnorm(25*5, 200,100)
samples <- rep(1:5,each =25)
my_data <- data.frame(samples, observations)

means <- my_data %>%
  group_by(samples) %>%
  summarize(sample_mean = mean(observations), sd=sd(observations))

#sample_means
ggplot(means, aes(x = samples, y =sample_mean))+
  geom_bar(stat="identity")

#error bars added
ggplot(means, aes(x = samples, y =sample_mean))+
  geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=sample_mean-sd, ymax=sample_mean+sd))
```



As sample size increases, statistics better approximate population parameters.  
```{r}
sample_size <- c(2,5,10,50,100)

sim_sample_means <- c()
for(i in 1:length(sample_size)){
  observations <- rnorm(sample_size[i]*10000,10,5)
  samples <- rep(1:10000, each = sample_size[i])
  my_data <- data.frame(samples,observations)
  summarized_data <- my_data %>%
    group_by(samples) %>%
    summarize(sample_means = mean(observations))
  
  sim_sample_means[i] <- mean(summarized_data$sample_means)
}
sim_data <- data.frame(sample_size, sim_sample_means)
ggplot(sim_data, aes(x=sample_size, y=sim_sample_means, group=1))+
  geom_point()+
    geom_smooth()
```


By using the "N-1" formula corrector to calculate the standard deviation of samples, we are able to arrive at unbiased estimates of the population standard deviation. 
```{r}
true_sd<-function(x){
  sum<-0
  for (i in x){
    sum<-((i-mean(x))^2)+sum
  }
  sqrt(sum/length(x))
}

sim_sample_sd <- c()
sim_sample_N<-c()
for(i in 1:length(sample_sizes)){
  observations <- rnorm(sample_size[i]*10000,10,5)
  samples <- rep(1:10000, each = sample_size[i])
  my_data <- data.frame(samples,observations)
  summarized_data <- my_data %>%
    group_by(samples) %>%
    summarize(sample_sd=sd(observations), sample_N=true_sd(observations))
  
  sim_sample_sd[i] <- mean(summarized_data$sample_sd)
  sim_sample_N[i]<-mean(summarized_data$sample_N)
}
sim_data <- data.frame(sample_size, sim_sample_sd, sim_sample_N)
ggplot(sim_data, aes(x=sample_size, y=sim_sample_sd, group=1))+
  geom_point()+
    geom_line() +
  coord_cartesian(ylim = c(0,10))

ggplot(sim_data, aes(x=sample_size, y=sim_sample_N), group=1)+
  geom_point()+
    geom_line() +
  coord_cartesian(ylim = c(0,10))
  
```
## Confidence in submission

On my own, Monte Carlo simulation lines of code would need to be much longer. Used RStats Method course answer key to condense samples and add in additional vectors to store mean of means and mean of standard deviations. 
Problem 1/2 - 90
Problem 3 - 60
Problem 4 - 60 

