---
title: "Lab 7"
author: KSRM
output: html_document
---

## Confidence in Submission

Problem 1 - 70 - Need to confirm interpretation of test. 
Problem 2 - 

Problem 1 - Given 50 trials and a 60% success rate, does the binomial test indicate that it is probable or improbable that chance alone played a part ? 

It is improbable that the test-taker was guessing. Based on the binomial distribution, only about 10% of the time would it be possible for the test-taker to guess 60% of the questions correctly. 
```{r}
library(purrr)
x <- 30
y <- 50
map2(x, y, alternative = "greater", .f = binom.test)


test_results <- binom.test((.60*50), 50, alternative = "greater")

# x - favorable or successful outcomes
# n - number of trials
# alternative = greater
# p = p value

test_results
test_results$p.value
```

Problem 2 - How many true-false questions does it take to ensure that chance alone cannot produce a score over 55% ? 

In order to prevent even one test-taker from achieving a score greater than 55% by chance, an examiner would need to use at least 575 questions on the test.  

```{r}
total.questions <- seq(100, 800, 25)
#default p-value is 0.5
percent.correct <- round(total.questions*.55)

results <- map2(.x = percent.correct, .y = total.questions, alternative = "greater", .f = binom.test)
p_values <- unlist(lapply(results, `[`, 3))

plot(x = total.questions, y = p_values, cex = 0.5, pch = 16, ylim = c(0,.25), asp = 0)
abline(h = 0.0099, v = 0, col = "red", lty = 2)#produce horizontal line for p_value of 0.05

df <- data.frame(total.questions, p_values)
df

```

Problem 3 - 

note - for the second part of the problem I think binom.test will be run for a 75% chance score 
```{r}


```

